Title

### 2016-11-16 paper.tex
first structure
structure
Pre-alpha version of kernels for structures. TO CHECK, but I'll do it tomorrow.

\section{Introduction}
...

>>>>

\section{Introduction}
In different real-world domains, it may be easy to encode examples in a structured form. For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds. Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are liked.
In these cases, specific machine learning techniques have to be adopted.
Kernel methods are one option, where it suffices to adopt a kernel function defined for the kind of data under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.

With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand. The values of these hyper-parameters can strongly affect the predictive performance of the method.
Usually, these parameters are:
\begin{enumerate}
 \item the choice of the kernel to adopt;
 \item the hyper-parameters of the selected kernel;
 \item the hyper-parameters of the learning algorithm.
\end{enumerate}
One commonly adopted and simple approach to fix these parameters is to fix a-priori some possible values for each parameter, and to test each possible combination on a validation set. This approach is commonly referred to as grid-search (from the parameter grid).
Then, only the best combination is used to predict the test set, in order to produce an unbiased error estimation of the method (if necessary).
In particular, for each point in the grid, a learning procedure have to be computed. In the case of kernel algorithms, a different kernel matrix has to be computed for the hyper-parameters at points 1 and 2.
This procedure may be very time consuming.
A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
\section{Kernel for structures and Multiple Kernel Learning}
When dealing with structured data, the choice of the kernel to adopt is a key step. Depending on the type of data under consideration, different proposals are available in literature, each one with a different tradeoff between predictive performance and computational time (of course, this tradeoff depends from the considered task).
In this paper we focus on graphs, i.e. we consider each example to be a different graph.
In this case, there are several graph kernels defined in literature based on random walks, shortest paths or subgraphs up to a fixed size[TODO]. The problem with these kernels is the high computational complexity, that makes them unapplicable to several real-world datasets.
Recently, different almost linear time graph kernels have been defined in literature, and these are the ones we focus o in this paper.
In the following we will give some details about the considered alternatives.
\textcolor{red}{TODO}\\
\begin{itemize}
 \item WL
 \item NSPDK
 \item ODD$_{ST}$
\end{itemize}

...

\section{Our framework}
...

\section{Experimental Results}
...

\section{Conclusion}
...
